\Title

### 2019-06-10 manuscript/manuscript.tex
Add publication DOI reserved by Oxford

\title{\Title}
\author{\AuthorAffil}
\date{
    \normalsize
    Accepted 2019 June 05. Received 2019 May 10; in original form 2018 December 29
    \\[0.4cm]
    This is a pre-copyedited, author-produced PDF of an article accepted for
    publication in \textit{Geophysical Journal International} following peer review.
    The version of record
    ``\textit{INSERT COMPLETE CITATION INFORMATION HERE}''
    is available online at: \href{https://doi.org/XXXXXXX}{doi.org/XXXXXX}
}
\maketitle

>>>>

\title{\Title}
\author{\AuthorAffil}
\date{
    \normalsize
    Accepted 2019 June 05. Received 2019 May 10; in original form 2018 December 29
    \\[0.4cm]
    This is a pre-copyedited, author-produced PDF of an article accepted for
    publication in \textit{Geophysical Journal International} following peer review.
    The version of record
    ``\textit{INSERT COMPLETE CITATION INFORMATION HERE}''
    is available online at: \href{https://doi.org/10.1093/gji/ggz277}{doi.org/10.1093/gji/ggz277}
}
\maketitle
